---
title: 'AFS and deforestation: analysis via propensity score matching for Amazon and Cerrado'
author: "Thiago Balbo Batista"
date: "2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Pre-analysis

### Packages:
```{r libraries, echo=FALSE}

library(cobalt)
library(ggplot2)
library(MatchIt)
library(readxl)

```

### Setting the database

```{r libraries, echo=FALSE}

# Importing the database:

Base <- read_excel("Base_Diss.xlsx", sheet = 11)

# Creating new covariates:

Base['PRECTOT2'] <- Base$PRECTOT ^ 2
Base['T2'] <- Base$T2M ^ 2


attach(Base)


```


### Propensity Score Matching (PSM): Treatments

The Propensity Score Matching (PSM) requires that we separate the sample between
the treatment and control group, depending on the problem, hypothesis, and
objective of the study. In this project, the hypothesis is that the expansion of Agroforestry Systems (AFS) in area, between the years 2006 and 2017, may have  
contained the agricultural land expansion on forest land, therefore, the AFS 
would have reduced the deforestation in the Amazon and Cerrado biomes.

So, as the literature do not define the required area expansion to produce 
effects on deforestation, I define four criterias to construct the treatment
group of Brazilian municipalities (only those with positive percentual expansion):

- Municipalities that show any increase above zero hectares between the years 2006 and 2017.

-75% of the municipalities with the highest percentage growth of AFS (higher 
than the first quartile of the sample).

-50% of the municipalities with the highest percentage growth of AFS (higher 
than the second quartile of the sample).

-25% of the municipalities with the highest percentage growth of AFS (higher 
than the third quartile of the sample).

The graphics showing the kernel distribution of treatment and control groups composed by municipalities are designed below:


```{r treatment graphics, echo=FALSE}

dens_exp <- density(Exp)


# First Treatment:

dd <- with(dens_exp, data.frame(x, y))
qplot(x, y, data = dd, geom = "line") + 
  geom_ribbon(data = subset(dd, x >= 0), aes(ymax = y), ymin =0,
    fill = "green", colour = NA, alpha =0.5) + 
      scale_x_continuous(breaks = seq(0, 5000, by = 500), limits = c(0,5000))+
       labs(x = "AFS growth (%) per municipality", y = "Density") +
         ggtitle("Agroforestry Systems Growth in hectares (%)" ) +
             theme(plot.title = element_text(hjust = 0.5))

## Second Treatment:

dd <- with(dens_exp, data.frame(x, y))
qplot(x, y, data = dd, geom = "line") + 
  geom_ribbon(data = subset(dd, x >= 57), aes(ymax = y), ymin =0,
    fill = "green", colour = NA, alpha =0.5) + 
      scale_x_continuous(breaks = seq(57, 5000, by = 502), limits = c(0,5000)) +
        labs(x = "AFS growth (%) per municipality", y = "Density") +
         ggtitle("Agroforestry Systems Growth in hectares (%)" ) +
             theme(plot.title = element_text(hjust = 0.5)) 

## Third Treatment:

dd <- with(dens_exp, data.frame(x, y))
qplot(x, y, data = dd, geom = "line") + 
  geom_ribbon(data = subset(dd, x >= 215), aes(ymax = y), ymin =0,
    fill = "green", colour = NA, alpha =0.5) + 
      scale_x_continuous(breaks = seq(215, 5000, by = 504), limits = c(0,5000))+
       labs(x = "AFS growth (%) per municipality", y = "Density") +
         ggtitle("Agroforestry Systems Growth in hectares (%)" ) +
             theme(plot.title = element_text(hjust = 0.5)) 


## Fourth Treatment:

dd <- with(dens_exp, data.frame(x, y))
qplot(x, y, data = dd, geom = "line") + 
  geom_ribbon(data = subset(dd, x >= 596), aes(ymax = y), ymin =0,
    fill = "green", colour = NA, alpha =0.5) + 
      scale_x_continuous(breaks = seq(596, 5000, by = 508), limits = c(0,5000))+
        labs(x = "AFS growth (%) per municipality", y = "Density") +
         ggtitle("Agroforestry Systems Growth in hectares (%)" ) +
             theme(plot.title = element_text(hjust = 0.5)) 

```

## Analysis

### First treatment

#### Unmatched sample

```{r Unmatched sample, echo=FALSE}

# Results: Unmatched sample
 
# 2017

mod_un_17 <- lm(Desm_2017 ~ Tratamento, data = Base )

summary(mod_un_17)

mod_un_c_17 <- lm(Desm_2017 ~ Tratamento + Rec.Hid + Prop + Educ + Financ +
        Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base )

summary(mod_un_c_17)


# 2018

mod_un_18 <- lm(Desm_2018 ~ Tratamento, data = Base )

summary(mod_un_18)

mod_un_c_18 <- lm(Desm_2018 ~ Tratamento + Rec.Hid + Prop + Educ + Financ + 
      Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base )

summary(mod_un_c_18)

# 2019

mod_un_19 <- lm(Desm_2019 ~ Tratamento, data = Base )

summary(mod_un_19)

mod_un_c_19 <- lm(Desm_2019 ~ Tratamento + Rec.Hid + Prop + Educ + Financ +  Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base )

summary(mod_un_c_19)

```

#### Matching - Nearest Neighbor (NN) 1:1 - caliper: 0.25 - With Replacement

```{r Matching - NN 1:1 - caliper: 0.25, echo=FALSE}

# Matching:

m1 <- matchit(Tratamento ~ Rec.Hid + Prop + Educ + Financ + Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base, caliper = 0.25, 
                     method = 'nearest', discard = 'treat', replace = TRUE)

summary(m1)


# The Overlap

k1 <- bal.plot(m1, var.name = "distance", which = "both", mirror = FALSE)
k1

# Covariates Balance

b1 <- love.plot(m1, stats = c("mean.diffs", "variance.ratios"), thresholds = c(m = 0.1, v = 2), abs = TRUE, binary = "std", var.order = "unadjusted")


# ATT Result

# 2017

m1_df <- match.data(m1)

mod_1_2017 <- lm(Desm_2017 ~ Tratamento + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m1_df, weights = weights)

summary(mod_1_2017)

# 2018

mod_1_2018 <- lm(Desm_2018 ~ Tratamento + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m1_df, weights = weights)

summary(mod_1_2018)

# 2019

mod_1_2019 <- lm(Desm_2019 ~ Tratamento + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m1_df, weights = weights)

summary(mod_1_2019)


```

### Matching - Nearest Neighbor (NN) 1:1 - caliper: 0.10 - With Replacement

```{r Matching - NN 1:1 - caliper: 0.10, echo=FALSE}

# Matching:

m2 <- matchit(Tratamento ~ Rec.Hid + Prop + Educ + Financ + Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base, caliper = 0.10, 
                     method = 'nearest', discard = 'treat', replace = TRUE)

summary(m2)


# The Overlap

k2 <- bal.plot(m1, var.name = "distance", which = "both", mirror = FALSE)
k2

# Covariates Balance

b2 <- love.plot(m1, stats = c("mean.diffs", "variance.ratios"), thresholds = c(m = 0.1, v = 2), abs = TRUE, binary = "std", var.order = "unadjusted")


# ATT Result

# 2017

m2_df <- match.data(m2)

mod_2_2017 <- lm(Desm_2017 ~ Tratamento + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m2_df, weights = weights)

summary(mod_2_2017)

# 2018

mod_2_2018 <- lm(Desm_2018 ~ Tratamento + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m2_df, weights = weights)

summary(mod_2_2018)

# 2019

mod_2_2019 <- lm(Desm_2019 ~ Tratamento + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m2_df, weights = weights)

summary(mod_2_2019)

```

#### Matching - Nearest Neighbor (NN) 2:1 - caliper: 0.25 - With Replacement

```{r Matching - NN 2:1 - caliper: 0.25, echo=FALSE}

# Matching:

m3 <- matchit(Tratamento ~ Rec.Hid + Prop + Educ + Financ + Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base, caliper = 0.25, 
                     method = 'nearest', discard = 'treat', replace = TRUE, 
                        ratio = 2)

summary(m3)


# The Overlap

k3 <- bal.plot(m1, var.name = "distance", which = "both", mirror = FALSE)
k3

# Covariates Balance

b3 <- love.plot(m1, stats = c("mean.diffs", "variance.ratios"), thresholds = c(m = 0.1, v = 2), abs = TRUE, binary = "std", var.order = "unadjusted")


# ATT Result

# 2017

m3_df <- match.data(m3)

mod_3_2017 <- lm(Desm_2017 ~ Tratamento + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m3_df, weights = weights)

summary(mod_3_2017)

# 2018

mod_3_2018 <- lm(Desm_2018 ~ Tratamento + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m3_df, weights = weights)

summary(mod_3_2018)

# 2019

mod_3_2019 <- lm(Desm_2019 ~ Tratamento + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m3_df, weights = weights)

summary(mod_3_2019)

```

#### Matching - Nearest Neighbor (NN) 2:1 - caliper: 0.10 - With Replacement

```{r Matching - NN 2:1 - caliper: 0.10, echo=FALSE}

# Matching:

m4 <- matchit(Tratamento ~ Rec.Hid + Prop + Educ + Financ + Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base, caliper = 0.10, 
                     method = 'nearest', discard = 'treat', replace = TRUE, 
                        ratio = 2)

summary(m4)


# The Overlap

k4 <- bal.plot(m1, var.name = "distance", which = "both", mirror = FALSE)
k4

# Covariates Balance

b4 <- love.plot(m1, stats = c("mean.diffs", "variance.ratios"), thresholds = c(m = 0.1, v = 2), abs = TRUE, binary = "std", var.order = "unadjusted")


# ATT Result

# 2017

m4_df <- match.data(m4)

mod_4_2017 <- lm(Desm_2017 ~ Tratamento + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m4_df, weights = weights)

summary(mod_4_2017)

# 2018

mod_4_2018 <- lm(Desm_2018 ~ Tratamento + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m4_df, weights = weights)

summary(mod_4_2018)

# 2019

mod_4_2019 <- lm(Desm_2019 ~ Tratamento + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m4_df, weights = weights)

summary(mod_4_2019)


```


### Second Treatment

#### Unmatched sample

```{r Unmatched sample, echo=FALSE}

# Results: Unmatched sample
 
# 2017

mod_un_17_Q1 <- lm(Desm_2017 ~ Tratamento_Q1, data = Base )

summary(mod_un_17_Q1)

mod_un_c_17_Q1 <- lm(Desm_2017 ~  Tratamento_Q1 + Rec.Hid + Prop + Educ + Financ +
        Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base )

summary(mod_un_c_17_Q1)


# 2018

mod_un_18_Q1 <- lm(Desm_2018 ~  Tratamento_Q1, data = Base )

summary(mod_un_18_Q1)

mod_un_c_18_Q1 <- lm(Desm_2018 ~ Tratamento_Q1 + Rec.Hid + Prop + Educ + Financ + 
      Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base )

summary(mod_un_c_18_Q1)

# 2019

mod_un_19_Q1 <- lm(Desm_2019 ~ Tratamento_Q1, data = Base )

summary(mod_un_19_Q1)

mod_un_c_19_Q1 <- lm(Desm_2019 ~ Tratamento_Q1 + Rec.Hid + Prop + Educ + Financ +  Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base )

summary(mod_un_c_19_Q1)

```

#### Matching - Nearest Neighbor (NN) 1:1 - caliper: 0.25 - With Replacement

```{r Matching - NN 1:1 - caliper: 0.25, echo=FALSE}

# Matching:

m5 <- matchit(Tratamento_Q1 ~ Rec.Hid + Prop + Educ + Financ + Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base, caliper = 0.25, 
                     method = 'nearest', discard = 'treat', replace = TRUE)

summary(m5)


# The Overlap

k5 <- bal.plot(m5, var.name = "distance", which = "both", mirror = FALSE)
k5

# Covariates Balance

b5 <- love.plot(m5, stats = c("mean.diffs", "variance.ratios"), thresholds = c(m = 0.1, v = 2), abs = TRUE, binary = "std", var.order = "unadjusted")


# ATT Result

# 2017

m5_df <- match.data(m5)

mod_5_2017 <- lm(Desm_2017 ~ Tratamento_Q1 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m5_df, weights = weights)

summary(mod_5_2017)

# 2018

mod_5_2018 <- lm(Desm_2018 ~ Tratamento_Q1 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m5_df, weights = weights)

summary(mod_5_2018)

# 2019

mod_5_2019 <- lm(Desm_2019 ~ Tratamento_Q1 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m5_df, weights = weights)

summary(mod_5_2019)


```

### Matching - Nearest Neighbor (NN) 1:1 - caliper: 0.10 - With Replacement

```{r Matching - NN 1:1 - caliper: 0.10, echo=FALSE}

# Matching:

m6 <- matchit(Tratamento_Q1 ~ Rec.Hid + Prop + Educ + Financ + Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base, caliper = 0.10, 
                     method = 'nearest', discard = 'treat', replace = TRUE)

summary(m6)


# The Overlap

k6 <- bal.plot(m1, var.name = "distance", which = "both", mirror = FALSE)
k6

# Covariates Balance

b6 <- love.plot(m1, stats = c("mean.diffs", "variance.ratios"), thresholds = c(m = 0.1, v = 2), abs = TRUE, binary = "std", var.order = "unadjusted")


# ATT Result

# 2017

m6_df <- match.data(m6)

mod_6_2017 <- lm(Desm_2017 ~ Tratamento_Q1 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m6_df, weights = weights)

summary(mod_6_2017)

# 2018

mod_6_2018 <- lm(Desm_2018 ~ Tratamento_Q1 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m6_df, weights = weights)

summary(mod_6_2018)

# 2019

mod_6_2019 <- lm(Desm_2019 ~ Tratamento_Q1 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m6_df, weights = weights)

summary(mod_6_2019)

```

#### Matching - Nearest Neighbor (NN) 2:1 - caliper: 0.25 - With Replacement

```{r Matching - NN 2:1 - caliper: 0.25, echo=FALSE}

# Matching:

m7 <- matchit(Tratamento_Q1 ~ Rec.Hid + Prop + Educ + Financ + Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base, caliper = 0.25, 
                     method = 'nearest', discard = 'treat', replace = TRUE, 
                        ratio = 2)

summary(m7)


# The Overlap

k7 <- bal.plot(m1, var.name = "distance", which = "both", mirror = FALSE)
k7

# Covariates Balance

b7 <- love.plot(m1, stats = c("mean.diffs", "variance.ratios"), thresholds = c(m = 0.1, v = 2), abs = TRUE, binary = "std", var.order = "unadjusted")


# ATT Result

# 2017

m7_df <- match.data(m7)

mod_7_2017 <- lm(Desm_2017 ~ Tratamento_Q1 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m7_df, weights = weights)

summary(mod_7_2017)

# 2018

mod_7_2018 <- lm(Desm_2018 ~ Tratamento_Q1 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m7_df, weights = weights)

summary(mod_7_2018)

# 2019

mod_7_2019 <- lm(Desm_2019 ~ Tratamento_Q1 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m7_df, weights = weights)

summary(mod_7_2019)

```

#### Matching - Nearest Neighbor (NN) 2:1 - caliper: 0.10 - With Replacement

```{r Matching - NN 2:1 - caliper: 0.10, echo=FALSE}

# Matching:

m8 <- matchit(Tratamento_Q1 ~ Rec.Hid + Prop + Educ + Financ + Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base, caliper = 0.10, 
                     method = 'nearest', discard = 'treat', replace = TRUE, 
                        ratio = 2)

summary(m8)


# The Overlap

k8 <- bal.plot(m1, var.name = "distance", which = "both", mirror = FALSE)
k8

# Covariates Balance

b8 <- love.plot(m1, stats = c("mean.diffs", "variance.ratios"), thresholds = c(m = 0.1, v = 2), abs = TRUE, binary = "std", var.order = "unadjusted")


# ATT Result

# 2017

m8_df <- match.data(m8)

mod_8_2017 <- lm(Desm_2017 ~ Tratamento_Q1 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m8_df, weights = weights)

summary(mod_8_2017)

# 2018

mod_8_2018 <- lm(Desm_2018 ~ Tratamento_Q1 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m8_df, weights = weights)

summary(mod_8_2018)

# 2019

mod_8_2019 <- lm(Desm_2019 ~ Tratamento_Q1 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m8_df, weights = weights)

summary(mod_8_2019)

```



### Third Treatment

#### Unmatched sample

```{r Unmatched sample, echo=FALSE}

# Results: Unmatched sample
 
# 2017

mod_un_17_Q2 <- lm(Desm_2017 ~ Tratamento_Q2, data = Base )

summary(mod_un_17_Q2)

mod_un_c_17_Q2 <- lm(Desm_2017 ~  Tratamento_Q2 + Rec.Hid + Prop + Educ + Financ +
        Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base )

summary(mod_un_c_17_Q2)


# 2018

mod_un_18_Q2 <- lm(Desm_2018 ~  Tratamento_Q2, data = Base )

summary(mod_un_18_Q2)

mod_un_c_18_Q2 <- lm(Desm_2018 ~ Tratamento_Q2 + Rec.Hid + Prop + Educ + Financ + 
      Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base )

summary(mod_un_c_18_Q2)

# 2019

mod_un_19_Q2 <- lm(Desm_2019 ~ Tratamento_Q2, data = Base )

summary(mod_un_19_Q2)

mod_un_c_19_Q2 <- lm(Desm_2019 ~ Tratamento_Q2 + Rec.Hid + Prop + Educ + Financ +  Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base )

summary(mod_un_c_19_Q2)

```

#### Matching - Nearest Neighbor (NN) 1:1 - caliper: 0.25 - With Replacement

```{r Matching - NN 1:1 - caliper: 0.25, echo=FALSE}

# Matching:

m9 <- matchit(Tratamento_Q2 ~ Rec.Hid + Prop + Educ + Financ + Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base, caliper = 0.25, 
                     method = 'nearest', discard = 'treat', replace = TRUE)

summary(m9)


# The Overlap

k9 <- bal.plot(m9, var.name = "distance", which = "both", mirror = FALSE)
k9

# Covariates Balance

b9 <- love.plot(m9, stats = c("mean.diffs", "variance.ratios"), thresholds = c(m = 0.1, v = 2), abs = TRUE, binary = "std", var.order = "unadjusted")


# ATT Result

# 2017

m9_df <- match.data(m9)

mod_9_2017 <- lm(Desm_2017 ~ Tratamento_Q2 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m9_df, weights = weights)

summary(mod_9_2017)

# 2018

mod_9_2018 <- lm(Desm_2018 ~ Tratamento_Q2 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m9_df, weights = weights)

summary(mod_9_2018)

# 2019

mod_9_2019 <- lm(Desm_2019 ~ Tratamento_Q2 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m9_df, weights = weights)

summary(mod_9_2019)


```

### Matching - Nearest Neighbor (NN) 1:1 - caliper: 0.10 - With Replacement

```{r Matching - NN 1:1 - caliper: 0.10, echo=FALSE}

# Matching:

m10 <- matchit(Tratamento_Q2 ~ Rec.Hid + Prop + Educ + Financ + Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base, caliper = 0.10, 
                     method = 'nearest', discard = 'treat', replace = TRUE)

summary(m10)


# The Overlap

k10 <- bal.plot(m1, var.name = "distance", which = "both", mirror = FALSE)
k10

# Covariates Balance

b10 <- love.plot(m1, stats = c("mean.diffs", "variance.ratios"), thresholds = c(m = 0.1, v = 2), abs = TRUE, binary = "std", var.order = "unadjusted")


# ATT Result

# 2017

m10_df <- match.data(m10)

mod_10_2017 <- lm(Desm_2017 ~ Tratamento_Q2 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m10_df, weights = weights)

summary(mod_10_2017)

# 2018

mod_10_2018 <- lm(Desm_2018 ~ Tratamento_Q2 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m10_df, weights = weights)

summary(mod_10_2018)

# 2019

mod_10_2019 <- lm(Desm_2019 ~ Tratamento_Q2 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m10_df, weights = weights)

summary(mod_10_2019)

```

#### Matching - Nearest Neighbor (NN) 2:1 - caliper: 0.25 - With Replacement

```{r Matching - NN 2:1 - caliper: 0.25, echo=FALSE}

# Matching:

m11 <- matchit(Tratamento_Q2 ~ Rec.Hid + Prop + Educ + Financ + Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base, caliper = 0.25, 
                     method = 'nearest', discard = 'treat', replace = TRUE, 
                        ratio = 2)

summary(m11)


# The Overlap

k11 <- bal.plot(m1, var.name = "distance", which = "both", mirror = FALSE)
k11

# Covariates Balance

b11 <- love.plot(m1, stats = c("mean.diffs", "variance.ratios"), thresholds = c(m = 0.1, v = 2), abs = TRUE, binary = "std", var.order = "unadjusted")


# ATT Result

# 2017

m11_df <- match.data(m11)

mod_11_2017 <- lm(Desm_2017 ~ Tratamento_Q2 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m11_df, weights = weights)

summary(mod_11_2017)

# 2018

mod_11_2018 <- lm(Desm_2018 ~ Tratamento_Q2 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m11_df, weights = weights)

summary(mod_11_2018)

# 2019

mod_11_2019 <- lm(Desm_2019 ~ Tratamento_Q2 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m11_df, weights = weights)

summary(mod_11_2019)

```

#### Matching - Nearest Neighbor (NN) 2:1 - caliper: 0.10 - With Replacement

```{r Matching - NN 2:1 - caliper: 0.10, echo=FALSE}

# Matching:

m12 <- matchit(Tratamento_Q2 ~ Rec.Hid + Prop + Educ + Financ + Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base, caliper = 0.10, 
                     method = 'nearest', discard = 'treat', replace = TRUE, 
                        ratio = 2)

summary(m12)


# The Overlap

k12 <- bal.plot(m1, var.name = "distance", which = "both", mirror = FALSE)
k12

# Covariates Balance

b12 <- love.plot(m1, stats = c("mean.diffs", "variance.ratios"), thresholds = c(m = 0.1, v = 2), abs = TRUE, binary = "std", var.order = "unadjusted")


# ATT Result

# 2017

m12_df <- match.data(m12)

mod_12_2017 <- lm(Desm_2017 ~ Tratamento_Q2 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m12_df, weights = weights)

summary(mod_12_2017)

# 2018

mod_12_2018 <- lm(Desm_2018 ~ Tratamento_Q2 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m12_df, weights = weights)

summary(mod_12_2018)

# 2019

mod_12_2019 <- lm(Desm_2019 ~ Tratamento_Q2 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m12_df, weights = weights)

summary(mod_12_2019)

```


### Fourth Treatment

#### Unmatched sample

```{r Unmatched sample, echo=FALSE}

# Results: Unmatched sample
 
# 2017

mod_un_17_Q3 <- lm(Desm_2017 ~ Tratamento_Q3, data = Base )

summary(mod_un_17_Q3)

mod_un_c_17_Q3 <- lm(Desm_2017 ~  Tratamento_Q3 + Rec.Hid + Prop + Educ + Financ +
        Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base )

summary(mod_un_c_17_Q3)


# 2018

mod_un_18_Q3 <- lm(Desm_2018 ~  Tratamento_Q3, data = Base )

summary(mod_un_18_Q3)

mod_un_c_18_Q3 <- lm(Desm_2018 ~ Tratamento_Q3 + Rec.Hid + Prop + Educ + Financ + 
      Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base )

summary(mod_un_c_18_Q3)

# 2019

mod_un_19_Q3 <- lm(Desm_2019 ~ Tratamento_Q3, data = Base )

summary(mod_un_19_Q3)

mod_un_c_19_Q3 <- lm(Desm_2019 ~ Tratamento_Q3 + Rec.Hid + Prop + Educ + Financ +  Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base )

summary(mod_un_c_19_Q3)

```

#### Matching - Nearest Neighbor (NN) 1:1 - caliper: 0.25 - With Replacement

```{r Matching - NN 1:1 - caliper: 0.25, echo=FALSE}

# Matching:

m13 <- matchit(Tratamento_Q3 ~ Rec.Hid + Prop + Educ + Financ + Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base, caliper = 0.25, 
                     method = 'nearest', discard = 'treat', replace = TRUE)

summary(m13)


# The Overlap

k13 <- bal.plot(m13, var.name = "distance", which = "both", mirror = FALSE)
k13

# Covariates Balance

b13 <- love.plot(m13, stats = c("mean.diffs", "variance.ratios"), thresholds = c(m = 0.1, v = 2), abs = TRUE, binary = "std", var.order = "unadjusted")


# ATT Result

# 2017

m13_df <- match.data(m13)

mod_13_2017 <- lm(Desm_2017 ~ Tratamento_Q3 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m13_df, weights = weights)

summary(mod_13_2017)

# 2018

mod_13_2018 <- lm(Desm_2018 ~ Tratamento_Q3 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m13_df, weights = weights)

summary(mod_13_2018)

# 2019

mod_13_2019 <- lm(Desm_2019 ~ Tratamento_Q3 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m13_df, weights = weights)

summary(mod_13_2019)


```

### Matching - Nearest Neighbor (NN) 1:1 - caliper: 0.10 - With Replacement

```{r Matching - NN 1:1 - caliper: 0.10, echo=FALSE}

# Matching:

m14 <- matchit(Tratamento_Q3 ~ Rec.Hid + Prop + Educ + Financ + Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base, caliper = 0.10, 
                     method = 'nearest', discard = 'treat', replace = TRUE)

summary(m14)


# The Overlap

k14 <- bal.plot(m1, var.name = "distance", which = "both", mirror = FALSE)
k14

# Covariates Balance

b14 <- love.plot(m1, stats = c("mean.diffs", "variance.ratios"), thresholds = c(m = 0.1, v = 2), abs = TRUE, binary = "std", var.order = "unadjusted")


# ATT Result

# 2017

m14_df <- match.data(m14)

mod_14_2017 <- lm(Desm_2017 ~ Tratamento_Q3 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m14_df, weights = weights)

summary(mod_14_2017)

# 2018

mod_14_2018 <- lm(Desm_2018 ~ Tratamento_Q3 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m14_df, weights = weights)

summary(mod_14_2018)

# 2019

mod_14_2019 <- lm(Desm_2019 ~ Tratamento_Q3 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m14_df, weights = weights)

summary(mod_14_2019)

```

#### Matching - Nearest Neighbor (NN) 2:1 - caliper: 0.25 - With Replacement

```{r Matching - NN 2:1 - caliper: 0.25, echo=FALSE}

# Matching:

m15 <- matchit(Tratamento_Q3 ~ Rec.Hid + Prop + Educ + Financ + Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base, caliper = 0.25, 
                     method = 'nearest', discard = 'treat', replace = TRUE, 
                        ratio = 2)

summary(m15)


# The Overlap

k15 <- bal.plot(m1, var.name = "distance", which = "both", mirror = FALSE)
k15

# Covariates Balance

b15 <- love.plot(m1, stats = c("mean.diffs", "variance.ratios"), thresholds = c(m = 0.1, v = 2), abs = TRUE, binary = "std", var.order = "unadjusted")


# ATT Result

# 2017

m15_df <- match.data(m15)

mod_15_2017 <- lm(Desm_2017 ~ Tratamento_Q3 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m15_df, weights = weights)

summary(mod_15_2017)

# 2018

mod_15_2018 <- lm(Desm_2018 ~ Tratamento_Q3 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m15_df, weights = weights)

summary(mod_15_2018)

# 2019

mod_15_2019 <- lm(Desm_2019 ~ Tratamento_Q3 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m15_df, weights = weights)

summary(mod_15_2019)

```

#### Matching - Nearest Neighbor (NN) 2:1 - caliper: 0.10 - With Replacement

```{r Matching - NN 2:1 - caliper: 0.10, echo=FALSE}

# Matching:

m16 <- matchit(Tratamento_Q3 ~ Rec.Hid + Prop + Educ + Financ + Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data = Base, caliper = 0.10, 
                     method = 'nearest', discard = 'treat', replace = TRUE, 
                        ratio = 2)

summary(m16)


# The Overlap

k16 <- bal.plot(m1, var.name = "distance", which = "both", mirror = FALSE)
k16

# Covariates Balance

b16 <- love.plot(m1, stats = c("mean.diffs", "variance.ratios"), thresholds = c(m = 0.1, v = 2), abs = TRUE, binary = "std", var.order = "unadjusted")


# ATT Result

# 2017

m16_df <- match.data(m16)

mod_16_2017 <- lm(Desm_2017 ~ Tratamento_Q3 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m16_df, weights = weights)

summary(mod_16_2017)

# 2018

mod_16_2018 <- lm(Desm_2018 ~ Tratamento_Q3 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m16_df, weights = weights)

summary(mod_16_2018)

# 2019

mod_16_2019 <- lm(Desm_2019 ~ Tratamento_Q3 + Rec.Hid + Prop + Educ + Financ +
                Assoc + Gen +  Pot.baixo + PRECTOT + T2M + PRECTOT2 + T2, data =                    m16_df, weights = weights)

summary(mod_16_2019)

```

### Results

As we can see above, in most of the estimations, the overlapping areas between the treatment and control groups get more adjusted after the matchings. Also, we can check that the covariables turn balanced after the matching because most of the absolute standardized mean differences are less than 10%, and the variance ratios get closer to one too.

Finally, most of the results do not show statistical significance. The exceptions are the results on the second treatment for the years 2017 and 2019, with coefficients of -0.107406 and -0.110650, respectively.These results mean that deforestation was lower in municipalities that AFS increased from 2006 to 2017.

Thus, the results do not show systematic evidence that the AFS expansion reduced deforestation on the Amazon and Cerrado biomes.

## Conclusion

These results show that the AFS expansion didn't reduce deforestation in the years from 2017 to 2019. Some of the possibilities are:

- The mitigation benefits of AFS are accomplished in the long-term, so if the expansion occurred around the year 2017, the benefits may happen in the next years. 

- The AFS implementations possibly improved agricultural productivity, so perhaps occurred agricultural land expansion to increase rural production.

- The AFS expansion may have occurred in a commercial model, thus do not necessarily pursue agroecological goals.






